Forecasting the age structure of the scientific workforce in Australia

### 2025-11-23 response.qmd

---
title: "Forecasting the age structure of the scientific workforce in Australia"
author: Response to reviewers
branding: false
linestretch: 1.2
bibliography: refs.bib
csl: apa-single-spaced.csl
format: 
  memo-typst: default # Use memo-pdf to use latex
filters:
  - reviewer.lua
pandoc-options:
---

@@

The $\beta_{k,t}$ values are principal component scores, so they are uncorrelated by construction. While it is possible for there to be some cross-correlations between the series at lags other than zero, these are usually not large enough for a multivariate model to give more accurate forecasts [see, @HU07] except in contrived simulated examples. On the other hand, @Aue2015 did use multivariate models to capture these cross-correlations, although they did not compare them on real data.

We have added a new paragraph along these lines in Section 2.

::: {.reviewer}
5. There is no mention of the statistical inference of the unknown parameters. For example, how were the unknown parameters in the model on pages 6 and 7 estimated?
:::

Functional principal component analysis [@HU07] was used to compute the principal component scores. All univariate ARIMA models were estimated using maximum likelihood estimation. The global ARIMA model was estimated using least squares estimation (as a full likelihood is somewhat difficult to compute across multiple series).

@@

This has now been noted in Section 2.

::: {.reviewer}
6. There is no simulation experiment to investigate the performance of the inference procedure.
:::

### 2025-11-23 age_structure_forecasts.qmd
Cleaned up bib

```{r}
#| label: tbl-disciplines
#| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences. The table lists their corresponding Detailed Fields.  "n.e.c." stands for "Not Elsewhere Classified."
tar_read(discipline_table)
```

>>>>

```{r}
#| label: tbl-disciplines
#| tbl-pos: "!hb"
#| tbl-cap: Classification of scientific disciplines, based on the ASCED Narrow Fields of Education within the Broad Field of Natural and Physical Sciences. The table lists their corresponding Detailed Fields.  "n.e.c." stands for "Not Elsewhere Classified."
tar_read(discipline_table)
```
